\bf Turkish Elections and Catastrophic Events

### 2021-12-12 paper/main.tex
Updates from Overleaf

\begin{subfigure}[t]{.49\textwidth}
    \includegraphics[scale=0.15]{paper/figures/earthquake_marmara2.jpeg}
	\caption{Marmara Earthquake}
	\end{subfigure}
	\begin{subfigure}[t]{.49\textwidth}
    \includegraphics[scale=0.3]{paper/figures/marmara_affected.jpeg}
	\caption{Regions Affected}
\end{subfigure}

>>>>

\begin{figure}[h]%
    \centering
    \subfloat[\centering Scene from Marmara Earthquake ]{{\includegraphics[width=7.1cm]{paper/figures/earthquake_marmara2.jpeg} }}%
    \qquad
    \subfloat[\centering Regions Affected]{{\includegraphics[width=7.1cm]{paper/figures/marmara_affected.jpeg} }}%
    \caption{Marmara Earthquake}%
    \label{fig:example}%
\end{figure}
